
\section{Research Plan}
In this section, a research plan is listed to achieve the previous proposed objective as well as some resources required for the research.
\subsection{Research Timetable}
In this section, a timetable of the research plan will be described. Basically, this research is planned to span the first one and a half year of my research.
\vskip 1cm
\textbf{\large{Semester-1 2014}}
\begin{itemize}
\item COMP9417 Data Mining and Machine Leanring course
\item Basic Bayesian theory learning
\item Review Bayesian Non-parametric Theory
\item Implenmentation of BNP model
\end{itemize}
\vskip 1cm
\textbf{\large{Semester-2 2014}}
\begin{itemize}
\item Literature Review
\item GSOE9400 Research Course
\item Review Active Learning Theory
\item Review sampling methods and inference theory on bayesian learning
\item Implementing the general coding framework and test on public dataset
\end{itemize}
\vskip 1cm
\textbf{\large{Semester-1 2015}}
\begin{itemize}
\item Develop the proposed sampling methods and implementation
\item Experiment of the proopsed learning theory and testing
\item Paper writing and publishing
\end{itemize}
\subsection{Resource Required}
In addition to the usual work space and equipment resources, some practical data set to test the performace is required. This could be supplied by NICTA as part of this research is related to one of its research project.

The only potential risk is that during the initial stage, many mathmatical hypothesis could be placed on the model to facilitate the theoretical inference, and the performance of the framework could be unsatisfied. But this could be address by modelling refine process. Finally, this framework will be upgraded for more complex problem thus the two main part should be loose-coupled to each other.   
%datasets
%programming tool
%books,papers on these methods